---
title: "Exam 2"
author: "Thomas Boswell"
date: "6/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exam 2

This is my submission for Exam 2 for Data Science in the Social World 

## College Scorecard Questions 

1. Please Clear the Environment in R 

```{r, echo = TRUE}

rm(list=ls(all=TRUE))

```

2. Load the College Scorecard Data and call it college_scorecard 

```{r, echo = TRUE}
# import data using rio, call college_scorecard
library(rio)
college_scorecard <- import("2021_exam2_data.xlsx", which = 4)
```

3. Provide Summary Statistics for the college_scorecard dataset

```{r, echo = TRUE}
# use stargazer, type text
library(stargazer)
stargazer(college_scorecard, type = "text")
```

4. Create a Smaller Dataset

```{r, echo = TRUE}
# use subset to call 2014, 2015 data, students from 4 year colleges, universities located in Texas and Lousiana, name data small scorecard 

library(tidyverse)
small_scorecard <- 
  college_scorecard %>%
  filter(year == "2014" | year == "2015") %>%
  filter(pred_degree_awarded_ipeds == 3) %>%
  filter(state_abbr == "TX" | state_abbr == "LA")
```

5. Collapse the Small Scorecard 

```{r}
even_smaller_scorecard <-
  small_scorecard %>% 
  group_by(state_abbr, inst_name) %>%
  summarize(across(where(is.numeric), sum)) %>% 
  summarize(across(where(is.numeric), mean))
```

6. Create a Bar Plot to demonstrate the percent of people working 

```{r}
library(ggplot2)
even_smaller_scorecard$
```

7. Unsure How to Complete these because I couldn't get the collapse to work. 

## Avocado Sales 

8. Load the avocados dataset in R, call it "avocados"

```{r, echo = TRUE}
avocados <- import("2021_exam_data.xlsx", which = 2)
```

9. Create a new variable called "year" that captures the year in which avocados were sold 

```{r, echo = TRUE}
library(lubridate)
avocados <-
  avocados %>%
  dplyr::mutate(year = lubridate::year(date))
```

10. Use WDI package to deflate the average_price variable. Call the new variable "deflated price_XXXX"

```{r, echo = TRUE}
library(WDI)
#Find the Deflator Data using WDI package 
deflator_data <- WDI(country = "all", indicator = c("NY.GDP.DEFL.ZS"),
                     start = 1960,
                     end = 2018,
                     extra = FALSE,
                     cache = NULL)

#Get USD

usd_deflator <- subset(deflator_data, country == "United States")

#Find the base year 
subset(usd_deflater, NY.GDP.DEFL.ZS == 100)

#Join the Deflation Data 
deflated_avocados <- left_join(avocados,
                           usd_deflator,
                           by=c("year"))

#Create a deflated avocado variable 
deflated_avocados$deflated_price_2015 <- deflated_avocados$average_price/(deflated_avocados$NY.GDP.DEFL.ZS/100)
```

11. Collapse the data frame to obtain the average deflated price of the avocados each year. 

```{r, echo = TRUE}
collapsed_avocados <-
  deflated_avocados %>%
  group_by(year) %>
  summarize(across(where(is.numeric), mean)

head(collapsed_avocados)
```

12. Reshape the deflated collapsed_avocados data frame wide call wide avocados 

```{r}
wide_avocados <-
  collapsed_avocados%>% 
  pivot_wider(id_cols = c("total_volume"),
               names_from = "year",
               values_from = "deflated_prices",
              names_prefix = "year_")

head(wide_avocados)
```

13. Label your variables in the wide_avocados df

```{r}
# label packages 
install.packages("labelled")
library(labelled)

# label our data 
var_label(wide_avocados)<- list('year_2015' = "2015 year",
      'year_2016' = "2016 year"
      'year_2017' = "2017 year"
      'year_2018' = "2018 year"
      'total_volume = "Volume Sold",

```

14. Load the training dataset in R. Call it training 

```{r}
training <- import("2021_exam2_data.xlsx", which = 3)
```

15. Reshape the training data 

```{r}
training_long <-
  pivot_longer(cols = starts_with("re_"),
names_to = "year", 
names_prefix = "re_",
values_to = "real_deflated_earnings")
```

16-19. Incomplete 